Covariate analysis of CMC RNASeq data reprocessed with Star-Feature counts pipeline (ACC and DLPFC with TMM normlaisation and SVA)

### 2017-01-10 code/Rmd/CMC_ACC_And_DLPFC_StarAligned_TMM_SVA.Rmd
Minor modifications

### Estimate surrogate variables using SVA package
```{r svaAdjust}
MODEL0 = DM1$design[,-grep('Dx.Tissue',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL1 = DM1$design

## Calculate the number of surrogate variables
NUM.SV = sva::num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1,
                     method = 'be', seed = 123456, B = 20)

SURR.VAR = sva::sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0,
                    block = COVARIATES$Individual_ID, 
                    n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])

>>>>

### Estimate surrogate variables using SVA package
```{r svaAdjust}
MODEL0 = DM1$design[,-grep('Dx.Tissue',colnames(DM1$design))] # Get null model by removing variable of interest
MODEL0 = MODEL0[,linColumnFinder(MODEL0)$indepCols]
MODEL1 = DM1$design
MODEL1 = MODEL1[,linColumnFinder(MODEL1)$indepCols]

## Calculate the number of surrogate variables
source('../R/num.sv.R')
NUM.SV = num.sv(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1,
                method = 'be', seed = 123456, B = 20, tol = 1e-22)

SURR.VAR = sva::sva(VOOM.ADJUSTED.GENE_EXPRESSION$E, MODEL1, MODEL0,
                    n.sv = NUM.SV, B = 30)$sv
colnames(SURR.VAR) = paste0('SV',1:dim(SURR.VAR)[2])
